Hydras and Cie (Draft) \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-18 doc/JFLA2022/paper.tex
small changes

\begin{figure}[h]
  \centering
  \begin{itemize}
\item If $\alpha=0$, then $H'_\alpha (i)= i$ for any natural number $i$.
\item If $\alpha=\beta+1$, then 
$H'_\alpha(i)=H'_\beta(i+1)$ for any $i \in \mathbb{N}$
\item If $\alpha$ is a limit ordinal, then 
$H'_\alpha(i) = H'_{(\canonseq{\alpha}{i+1})}(k)$ for any $i\in \mathbb{N}$.
\end{itemize}
\vspace{4pt}
\inputsnippets{Hprime/HprimeDef}
\caption{The rapidly growing hierarchy $H'$}
\label{fig:Hprime}
\end{figure}

@@

\subsection{The Coq-community ecosystem}
\begin{todo}
Small presentation.
\end{todo}

In order to prove formally that the length of the considered
kind of battles is not given by a primitive recursive function, weused the formalisation of primitive recursive functions, part
of Russell O'Connor's contribution on G\"{o}del first incompleteness theorem \cite{OConnor05}. We chose to host and maintain this work in Coq-community. The pedagogical interest of this formalisation led us to add new examples and exercises on primtive recursive functions.

>>>>

\begin{figure}[h]
  \centering
  \begin{itemize}
\item If $\alpha=0$, then $H'_\alpha (i)= i$ for any natural number $i$.
\item If $\alpha=\beta+1$, then 
$H'_\alpha(i)=H'_\beta(i+1)$ for any $i \in \mathbb{N}$
\item If $\alpha$ is a limit ordinal, then 
$H'_\alpha(i) = H'_{(\canonseq{\alpha}{i+1})}(k)$ for any $i\in \mathbb{N}$.
\end{itemize}
\vspace{4pt}
\inputsnippets{Hprime/HprimeDef}
\caption{The rapidly growing hierarchy $H'$ of arithmetic functions}
\label{fig:Hprime}
\end{figure}

@@

\subsection{The Coq-Community ecosystem}
\begin{todo}
Small presentation.
\end{todo}

In order to prove formally that the length of the considered
kind of battles is not given by a primitive recursive function, weused the formalisation of primitive recursive functions, part
of Russell O'Connor's contribution on G\"{o}del first incompleteness theorem \cite{OConnor05}. Computability is a key topic in Computer Science teaching. Moreover O'Conors library is a nice illustation on dependently typed functions, so we chose to devote a full chapter to this formalisation, with comments on the definitions and proofs, [counter]-examples and exercises.
